Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Total changes, plural
Figure layout
Formatting

\newcommand{\match}{\mathit{match}}
\newcommand{\timeSlot}{\mathit{timeSlot}}
\newcommand{\state}{\mathit{state}}
\newcommand{\change}{\mathit{change}}
\newcommand{\totalChange}{\mathit{totalChange}}
\newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
\newcommand{\modMatch}{\mathit{modMatch}}
\newcommand{\position}{\mathit{position}}
\newcommand{\imbalance}{\mathit{imbalance}}
\newcommand{\maxImbalance}{\mathit{maxImbalance}}

@@

A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$ and then is in a match in the next flight $i+1$. This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
    & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
\end{flalign}

%\vspace{-6mm}
\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
\vspace{-25mm}
\caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey timeslots. The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}
\label{skipper5}
\end{figure}

\noindent
We are now in a position to model criteria 1 (each skipper sails against every other skipper) and optimisation criteria 10 (minimise boat changes).  In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
match-perspective of the schedule, using a two dimensional array of variables $\match$, where $\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match. Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e. $\match[{i,j}]$ is \emph{exactly} the same constrained variable as $\match[{j,i}]$.  Constraint (\ref{eq15}) states that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$ (i.e. $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.  Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e. $\modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.

@@

%
% optimisation criteria 10
%
\begin{flalign}
    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChange  \label{eq22} \\
& minimise(\totalBoatChanges) \label{eq23}
\end{flalign}

>>>>

\newcommand{\match}{\mathit{match}}
\newcommand{\timeSlot}{\mathit{timeSlot}}
\newcommand{\state}{\mathit{state}}
\newcommand{\change}{\mathit{change}}
\newcommand{\totalChanges}{\mathit{totalChanges}}
\newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
\newcommand{\modMatch}{\mathit{modMatch}}
\newcommand{\position}{\mathit{position}}
\newcommand{\imbalance}{\mathit{imbalance}}
\newcommand{\maxImbalance}{\mathit{maxImbalance}}

@@

A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$
and then is in a match in the next flight $i+1$. This is encoded using the
array of zero/one variables \ref{eq10}, and the constraint (\ref{eq11}), and
accumulated into $\totalChanges$ (\ref{eq12}).

\begin{flalign}
    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
    & \totalChanges = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
\end{flalign}

\begin{figure}[tb]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
\caption{A pictorial representation of a skipper (skipper 5) with multicoloured
state and grey timeslots. The schedule for skipper 5 is in bold and the
deterministic finite automata for criteria 4, 11 and 12 is drawn with state
$\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
in pink and $\END$ in red.}
\label{skipper5}
\end{figure}

We are now in a position to model criteria 1 (each skipper sails against every
other skipper) and optimisation criteria 10 (minimise boat changes).  In
\ref{eq13}, \ref{eq14} and \ref{eq15} we present a match perspective of the
schedule, using a two dimensional array of variables $\match$, where
$\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a
match. Only the half above the diagonal is represented, and the lower half is
made up of exactly the same variables, i.e. $\match[{i,j}]$ is \emph{exactly}
the same constrained variable as $\match[{j,i}]$. Constraint \ref{eq15} states
that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$
(i.e. $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time
slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time
slot is skipper $s[{i}]$).  Constraints \ref{eq16}, \ref{eq17} and \ref{eq18}
then convert this from time slots to flights, i.e.  $\modMatch[{i,j}]$ is the
flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally,
constraint \ref{eq19} ensures that each skipper's match occurs in different
flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows
to be all different also ensures that columns are all different.

@@

%
% optimisation criteria 10
%
\begin{flalign}
    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChanges  \label{eq22} \\
& minimise(\totalBoatChanges) \label{eq23}
\end{flalign}
